The Place of the Local Group in the Cosmic Web

### 2014-07-11 paper/main.tex
new figures in text
starting new paragraph in the introduction

%this paper.
In this Letter we study the large scale environment of LG 
analogues in the context of $\Lambda$CDM. We use the Bolshoi
simulation to explore in what structures they reside and if there is
any correlation or alignment with the cosmic web. The large scale
Environment is defined by the cosmic web components identified by
\citet{Tweb}, and we use the LG analogues computed by
\citet{lganalogues}.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_filament.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e1_sheet.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_filament.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_sheet.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_filament.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_sheet.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the unit
  vector linking the two halos, $\hat{r}$, and the eigenvectors
  defining the cosmic web.
    \label{fig:alignment}}  
\end{figure*}

@@

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. 
\label{table:web_type}}
\end{center}
\end{table}

>>>>

%Tweb definition
The environment definition we use in this Letter uses the tidal tensor
field.

%this paper.
In this Letter we study the large scale environment of LG 
analogues in the context of $\Lambda$CDM. We use the Bolshoi
simulation to explore in what structures they reside and if there is
any correlation or alignment with the cosmic web. The large scale
Environment is defined by the cosmic web components identified by
\citet{Tweb}, and we use the LG analogues computed by
\citet{lganalogues}. We pay spetial attention to quantify the kind of
environment that hosts LG pairs and their alignments with respect to
the prefered directions defined by the T-web.

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_nall_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_nall_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_nall_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal vector
$\hat{n}$, and the eigenvectors defining the cosmic web.
    \label{fig:alignment}}  
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_rall_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_rall_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_rall_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the unit
  vector linking the two halos, $\hat{r}$, and the eigenvectors
  defining the cosmic web.
    \label{fig:alignment_r}}  
\end{figure}

%% \begin{figure}
%% \begin{center}
%%   \includegraphics[width=0.48\textwidth]{scheme.pdf} 
%% \caption{Schematic picture of the strongest alignment tendencies in
%%   the the General and $2\sigma$-$3\sigma$ samples. The alignment
%%   between the peculiar velocities and the $\hat{e}_3$ eigenvector was
%%   reported in \citet{ForeroRomero2014} for all halos regardles of its
%%   mass. The flip in the alignment in the vector connecting the two
%%   dominant halos in pairs is a summary of the results in Figure
%%   \ref{fig:alignment}. 
%% \label{fig:scheme}}
%% \end{center}
%% \end{figure}

@@

\begin{table*}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. 
\label{table:web_type}}
\end{center}
\end{table*}
